An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
Update main.tex
change RFANN Robustness

	% \begin{table}[t]
	% 	\centering
	% 	\setlength{\abovecaptionskip}{0.05cm}
	% 	\caption{Time and space overhead of range filtering index construction}

	% 	\label{tab:Range Filtered}
	% 	\resizebox{\columnwidth}{!}{
	% 		\begin{tabular}{l l c c c c c }
	% 			\toprule
	% 			\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
	% 			\midrule
	% 			\multirow{3}{*}{DEEP} 
	% 			& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
	% 			& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
	% 			& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
	% 			% \cmidrule{1-7}
	% 			\midrule
	% 			\multirow{3}{*}{YT-Audio} 
	% 			& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
	% 			& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
	% 			& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
	% 			\midrule
	% 			\multirow{3}{*}{WIT} 
	% 			& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
	% 			& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
	% 			& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
	% 			% \cmidrule{1-7}
	% 			\bottomrule
	% 		\end{tabular}
	% 	}
	% \end{table}

@@

	\subsection{Range Filtering}
	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range-filtering algorithms.
	\subsubsection{Time and Space overhead of index construction.}
	%4.2.1

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{0cm}

		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

		\vspace{0.3cm}

		% 三图横排
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{Index construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{Index size}
			\label{fig:rangeFilter_ndex_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.31\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

		\caption{Time and space overhead of range filtering index construction}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

@@

	\textit{\textbf{Index construction time.}}
, SeRF achieves the fastest index construction time among the 5 algorithms. It incrementally builds the index in attribute order. It requires only a single pass and adds edges within local graphs. The structure is simple, with no redundant operations.

>>>>

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.05cm}
		\caption{Time and space overhead of range filtering index construction}

		\label{tab:Range Filtered}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{l l c c c c c }
				\toprule
				\textbf{Dataset} & \textbf{Metric} & \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{WinFilter} \\
				\midrule
				\multirow{3}{*}{DEEP} 
				& Index time(s)  & 4156 & 1128 & \textbf{189.89} & 7510 & 32843 \\
				& Index size(GB)  &  4.6 & 0.92 & \textbf{0.80} & 1.43 & 2.41  \\
				& Peak memory(GB) &  7.78 & 3.54 & \textbf{1.38} & 2.61 & 7.08   \\
				% \cmidrule{1-7}
				\midrule
				\multirow{3}{*}{YT-Audio} 
				& Index time(s)   & 15314 & 1039 & \textbf{187.20} & 5905 & 30904    \\
				& Index size(GB)    & 4.3 & \textbf{0.7} & 1.04 & 1.55 & 1.32  \\
				& Peak memory(GB)   & 7.5 & 3.16 & \textbf{1.57} & 2.97 & 6.95  \\
				\midrule
				\multirow{3}{*}{WIT} 
				& Index time(s)  & 29492 & 7068 & \textbf{828.12} & 28759 & 94909\\
				& Index size(GB) &  4.2 & \textbf{1.5 }& 15.34 & 8.71 & 1.59  \\
				& Peak memory(GB)  & 21.7 & \textbf{12.32} & 15.87 & 24.38 & 15.29\\
				% \cmidrule{1-7}
				\bottomrule
			\end{tabular}
		}
	\end{table}

@@

	\subsection{Range Filtering}
	Although the libraries and databases mentioned above can also implement range filtering, the results are poor, so we only compare 5 range-filtering algorithms.
	\subsubsection{Time and Space overhead of index construction.}

@@

	\textit{\textbf{Index construction time.}}
	As shown in Table \ref{tab:Range Filtered}, SeRF achieves the fastest index construction time among the 5 algorithms. It incrementally builds the index in attribute order. It requires only a single pass and adds edges within local graphs. The structure is simple, with no redundant operations.
